HTW E1

### 2024-03-17 Analysis/e1.qmd
remove toc for full page

---
title: "HTW E1"
author:
  - name: Thomas Gorman
    corresponding: true
categories: [Analyses, R, Bayesian]
page-layout: full
code-fold: true
cold-tools: true
lightbox: true
# execute: 
#   cache: true
keep-md: true
format:
  html: default
  # hikmah-manuscript-pdf:
  #   echo: false
  #   output-file: "hikmah-e1.pdf"
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #     - "Numbers=Proportional"
  #     - "Numbers=OldStyle"
  #   mathfont: "Libertinus Math"
  # hikmah-pdf:
  #   echo: false
  #   cite-method: citeproc
  #   output-file: "hikmah.pdf"
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #     - "Numbers=Proportional"
  #     - "Numbers=OldStyle"
  #   sansfont: "IBM Plex Sans"
  #   mathfont: "Libertinus Math"
  #   geometry:
  #     - top=1in     
  #     - bottom=1in  
  #     - left=1in    
  #     - right=1in  
  #     - heightrounded
  #   # linestretch: 1.05
  #   include-in-header:
  #     # The \everydisplay thing makes all math blocks use \small font
  #     text: |
  #       \usepackage{mathtools}
  #       \everydisplay\expandafter{\the\everydisplay\small}
  #       \usepackage{float}
  #       \floatplacement{figure}{H}
  #       \floatplacement{table}{H}
  # pdf: 
  #   echo: false
  #   documentclass: article
  #   papersize: a4
  #   geometry:
  #     - left=2cm
  #     - right=2cm
  #     - top=2cm
  #     - bottom=2cm
  ipynb: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-dir: "../_working"
    output-file: e1-hugo.md
  gfm:
    echo: true
    output-file: e1-gfm.md
  docusaurus-md:
    echo: true
    output-file: e1-docusaurus.md
#prefer-html: false
---

>>>>

---
title: "HTW E1"
author:
  - name: Thomas Gorman
    corresponding: true
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
code-fold: true
cold-tools: true
lightbox: true
# execute: 
#   cache: true
keep-md: true
format:
  html: default
  # hikmah-manuscript-pdf:
  #   echo: false
  #   output-file: "hikmah-e1.pdf"
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #     - "Numbers=Proportional"
  #     - "Numbers=OldStyle"
  #   mathfont: "Libertinus Math"
  # hikmah-pdf:
  #   echo: false
  #   cite-method: citeproc
  #   output-file: "hikmah.pdf"
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #     - "Numbers=Proportional"
  #     - "Numbers=OldStyle"
  #   sansfont: "IBM Plex Sans"
  #   mathfont: "Libertinus Math"
  #   geometry:
  #     - top=1in     
  #     - bottom=1in  
  #     - left=1in    
  #     - right=1in  
  #     - heightrounded
  #   # linestretch: 1.05
  #   include-in-header:
  #     # The \everydisplay thing makes all math blocks use \small font
  #     text: |
  #       \usepackage{mathtools}
  #       \everydisplay\expandafter{\the\everydisplay\small}
  #       \usepackage{float}
  #       \floatplacement{figure}{H}
  #       \floatplacement{table}{H}
  # pdf: 
  #   echo: false
  #   documentclass: article
  #   papersize: a4
  #   geometry:
  #     - left=2cm
  #     - right=2cm
  #     - top=2cm
  #     - bottom=2cm
  ipynb: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-dir: "../_working"
    output-file: e1-hugo.md
  gfm:
    echo: true
    output-file: e1-gfm.md
  docusaurus-md:
    echo: true
    output-file: e1-docusaurus.md
#prefer-html: false
---
